---
title: "Activity Brainstorm"
output: html_notebook
---


# Tasks overview  

**High level goals:**  
* Decide KPIs and timeframe  
* Decide platform focus (if any)  
* Decide cost effective expenditure (if any)  
* Confirm current capability and added benefits of ads, better API access  
* Confirm taks that can be automated  
* Confirm tasks that should not be automated  
* Design monitoring system  
* Confirm ability to store / manipulate historic data  
  
  
**Increase exposure:**  
* current climate activist network  
* new recruits to the cause  
  
  
**Focus:**  
* Reaching climate influencers  
* Activating new (climate) influencers  
* Activating existing (general) influencers  
  
  
**Curate:**  
* hashtags  
* topics  
* social media partners  
  
  
**Copy goals:**  
* For each category: decide hashtags, topics, social media partners  
  
  
**Corporate partner goals:**  
* List existing 
* List prospective  
* Engage IRL  
  
  
**Influencer goals:**  
* List existing 
* List prospective  
* Expand activated network  
* Engage IRL  
  
  


## Existing setup

```{r}
steps
```

```{r}
categories
```


