---
title: "Network Analysis"
output:
  html_document:
    output_dir: "html"
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    # css: ../../../styles.css
  pdf_document: default

---

# Intro
In this course you'll learn how to work with and visualize network data. You'll use the igraph package to create networks from edgelists and adjacency matrices. You'll also learn how to plot networks and their attributes. Then, you'll learn how to identify important vertices using measures like betweenness and degree. Next, this course covers network structures, including triangles and cliques. Next, you'll learn how to identify special relationships between vertices, using metrics like assortativity. Finally, you'll see how to create interactive network plots using threejs.



# Introduction to networks

In this chapter, you will be introduced to fundamental concepts in social network analysis. You will learn how to use the igraph R package to explore and analyze social network data as well as learning how to visualize networks.

## Creating an igraph object

Here you will learn how to create an igraph 'object' from data stored in an edgelist. The data are friendships in a group of students. You will also learn how to make a basic visualization of the network.

Each row of the friends dataframe represents an edge in the network.

Instructions
100 XP
Instructions
100 XP
Inspect the first few rows of the dataframe friends using the function head().
Create new object friends.mat from the dataframe friends using as.matrix().
Convert variable to an igraph object g using graph.edgelist().
Make a basic plot of the network using plot().

```{r}
# Load igraph
library(igraph)

# Inspect the first few rows of the dataframe 'friends'
head(friends)

# Convert friends dataframe to a matrix
friends.mat <- as.matrix(friends)

# Convert friends matrix to an igraph object
g <- graph.edgelist(friends.mat, directed = FALSE)


# Make a very basic plot of the network
plot(g)


```

## Counting vertices and edges

A lot of basic information about a network can be extracted from an igraph object. In this exercise you will learn how to count the vertices and edges from a network by applying several functions to the graph object g.

Each row of the friends dataframe represents an edge in the network.

Instructions
100 XP
Use V() and E() to view the vertices and edges respectively of the network.
Use gsize() to count the number of edges in a network.
Use gorder() to count the number of vertices in a network.

```{r}

```

